Stochastic Approximation Monte Carlo with a Dynamic Update Factor (SAD)

### 2018-11-07 papers/histogram/sad.tex

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/N500-lndos-comparison}
  \caption{Put this in the right place}
\end{figure}

@@

{\color{red} Both weight-based and transition matrix methods calculate
the density of states $D(E)$ for discrete energy
levels~\cite{haber2018performance}. For this reason, energy binning
becomes an important consideration for complex continous systems.
Energy bins are typically of uniform size for the entire energy
continuum~\cite{fasnacht2004adaptive}. Coarse binning yields fewer
energy states to explore but more time spent in each individual bin.
Fine binning yields more energy states to explore with less time spent
in each bin. Some methods such as AdaWL~\cite{koh2013dynamically}
employ a tunable mechanism for controlling the binning for low entropic
states in order to ensure the exploration of all energies. }

@@

\subsection{SAMC}
The Stochastic Approximation Monte Carlo (SAMC) algorithm addresses
the lack of convergence of Wang-Landau's approach with a simple
schedule by which the update factor $\gamma$ is continuously
decreased~\cite{liang2007stochastic, werlich2015stochastic,
  schneider2017convergence}.  The update factor is defined in the
original implementation~\cite{liang2007stochastic} in terms of an
arbitrary tunable parameter $t_0$.
\begin{align}
\gamma_{t}^{\text{SA}} =\frac{t_0}{\max(t_0,t)}
\end{align}
where as above $t$ is the number of moves that have been attempted.
The major advantage that SAMC offers is its proven convergence.
Provided the update factor satisfies
\begin{align}
\sum_{t=1}^\infty \gamma_{t} = \infty \quad\textrm{and}\quad
\sum_{t=1}^\infty \gamma_{t}^\zeta < \infty
\end{align}
where $\zeta \in \{1,2\}$, Liang has shown that the weights are proven
to converge to the true density of states~\cite{liang2006theory,
  liang2007stochastic}.  In addition, the energy range need not be
known a priori.  The time to converge depends only on the choice of
parameters $t_0$.  Unfortunately, there is no
prescription for finding an acceptable value for $t_0$, and
while the algorithm formally converges, for a poor choice of $t_0$
that convergence can be far too slow to be practical.

Werlich \emph{et al.} proposed scaling the SAMC $\gamma_t$ by a factor
$\gamma_0$.  While this may result in an improved rate of convergence,
it adds yet another parameter that must be empirically determined.

@@

@@

Figure~\ref{fig:gamma-vs-t} compares $\gamma_t$ for SAD, WL,
and SAMC.  The update factor
for WL remains high for many iterations, and then decreases very rapidly,
while the SAMC $\gamma_t$ remains constant before dropping as $1/t$.
The update factor for SAD in contrast fluctuates
dynamically around a value less than 1 for early MC moves
(while finding new energy states), before dropping in a \davidsays{similar
to SAD, but described after we see the plot}.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n500}
  \caption{The update factor $\gamma_t$ for $N=500$ versus iteration for three
    different methods: WL, SAMC, and SAD.
    method.}\label{fig:gamma-vs-t}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{The update factor $\gamma_t$ for $N=50$ versus iteration for three
    different methods: WL, SAMC, and SAD.  This is exciting because we
    have different MC moves (slow, etc).}
\end{figure}

@@

A significant advantage of SAD over other flat histogram methods is
that energy binning is solved dynamically. SAD should perform
independently for a reasonable range of binning because $\gamma \propto
\nicefrac{N_{E}}{t}$.  As the number of energy states found $N_{E}$
increases (fine binning), the time spent $t$ in each bin will decrease.
This argument explains why SAD should perform well for complex systems
in terms of binning. SAMC has a prefactor $\gamma_0$ to aid in a
similar way but this adds yet another parameter for the user to choose.

@@

\subsection{Convergence}
Although SAD determines the update factor ``dynamically'', the method
must still satisfy the SAMC convergence criteria. As in
Section~\ref{sec:samc-convergence} on the convergence for SAMC, we
will approximate the total entropy change using an integral.  We
integrate update factor from the last time an energy has been
discovered $t_L$ to some minimum time $t_{\min}$ necessary for
convergence.  This gives us a lower bound on the total entropy change
that can be acheived in $t_{\min}$ moves.
\begin{align}
\Delta S_{\text{tot}} &= \int_{t_L}^{t_{\min}}
     \frac{
       3\langle S\rangle + \frac{t}{t_L}
     }{
       3\langle S\rangle + \frac{t}{N_S}\frac{t}{t_L}
     } dt \\
&\approx N_S \ln\left(\frac{t_{\min}}{t_L}\right)
   + \Delta S_{\text{tot}} \left(1-\frac{t_L}{t_{\min}}\right)
\end{align}
where we assumed that $t_L\gg N_S\langle S\rangle$, which is to say
that it takes a long time to find all the interesting energy states.
Simplifying, we see that as $t_{\min} \rightarrow \infty$ then $\gamma
\rightarrow \infty$ satisfying the requirement for SAMC
convergence. We can solve for the minimum time
\begin{align}
\Delta S_{\text{tot}} \approx N_S \ln\left(\frac{t_{\min}}{t_L}\right)
+ \Delta S_{\text{tot}} \left(1-\frac{t_L}{t_{\min}}\right)
\end{align}
Solving for the minimum time necessary $t_{\min}$, we find that
\begin{align}
\frac{t_{\min}}{t_L} = e^{\frac{\langle S\rangle t_L}{t_{\min}}}
\end{align}
The solution for $t_{\min}$ can be written in terms of the Lambert-W function
\begin{align}
t_{\min} = \frac{3\langle S\rangle}{W(3\langle S\rangle e^{2\langle S\rangle})} t_L
\end{align}
For $\langle S\rangle \rightarrow 0$, we find that the minimum time
$t_{\min} \rightarrow t_L$ and for $\langle S\rangle \rightarrow \infty$,
we find that the minimum time $t_{\min} \rightarrow \frac{3}{2} t_L$.

We can examine the limiting cases for SAD and see that the behavior at
short times is analogous to the weight-based family algorithms $\gamma \approx 1$.
In the limit that the number of moves $t >> t_L$, $\gamma \approx \nicefrac{N_S}{t}$
which has a familiar 1/t form.

@@

For the square-well fluid, our simulations treat systems with a
well-width of $\lambda = 1.30$ and a filling fraction of
$\eta = 0.30$. We also explore various translation scales $\delta_0 = 0.005 and
0.05$. The simulations explore the
energy space of the systems at reduced temperatures of
$T_{\text{min}} = 0.2$ and $0.5$.  All simulations lead to the minimum important
energy $E_{\min}$ and maximum entropy energy $E_{\max}$
being calculated (with the exception of the WL methods where both
of these parameters are needed a priori).  In the sections below, we
examine the systems parameters impact on the convergence of the methods.

We use the average entropy error vs moves as a metric to compare
simulation runtimes and overall convergence. The overall accuracy
is determined by examining the fractional error of a particular method to
a `golden' standard. For each simulation, the `golden' standard is
SAMC for the best choice of $t_0$.
\begin{align}
\epsilon_\text{avg} = 1 - \bigg\lvert\frac{S_\text{method}}{S_\text{golden}}\bigg\rvert
\end{align}
Simulations that take more iterations to reach the same entropy error as a
different method take longer to converge. This behavior is seen in
Fig.~\ref{fig:N50-ff0.3-avg-error}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.30$ and $T_{\min} = 0.2$ with
  SAMC $t_0 = 10^5$ serving as the `golden' standard.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-slow.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.30$ and $T_{\min} = 0.2$ with
  SAMC $t_0 = 10^5$ from Fig.~\ref{fig:N50-ff0.3-avg-error}
  serving as the `golden' standard.}\label{fig:N50-ff0.3-avg-error-slow}
\end{figure}
%\begin{figure}
  %\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-fast.pdf}
  %\caption{The average entropy error for each method is shown for $\eta = 0.30$ with
  %SAMC followed by TMMC serving as the `golden'
  %standard.}\label{fig:N50-ff0.3-avg-error-fast}
%\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.30$ and $T_{\min} = 0.5$ with
  SAMC $t_0 = 10^6$ serving as the `golden' standard.}\label{fig:n500-ff0.3}
\end{figure}

\subsection{A periodic system with $\eta = 30\%$ and $N = 50$}

Figure~\ref{fig:N50-ff0.3-avg-error} shows the average entropy vs moves
for a system consisting of 50 atoms that are placed in a periodic
simple cubic unit cell with lattice constant chosen to give a $\eta =
0.30$.  These particles are randomly inserted into the system and
random moves are proposed (with a translation scale $\delta_0 = 0.05$).
For the $\eta = 30\%$ and $N = 50$ system, we explore the choice of
$\delta_0$ as a parameter. Smaller translation scales cause the given
method to take additional time to explore all energies. Ideal methods
should scale linearly with the $\delta_0$, that is, a decrease in the
translation scale should result in a proportional increase in
convergence time. However, as can be seen from
Fig.~\ref{fig:N50-ff0.3-avg-error-slow} SAMC methods that rapidly
converged for $\delta = 0.05$ do not proportionaly converge for a
translation scale of $\delta = 0.005$. We see that SAD handles
arbitrary translation scales and proportionaly converges based on the
translation scale that is chosen.

\subsection{A periodic system with $\eta = 30\%$ and $N = 500$}

A system is configured with dimensions $x = y = z = 19\sigma$.  A
filling fraction $\eta = 0.30$ is chosen which yields $N = 500$
particles in a cubical lattice system.  These particles are randomly inserted
into the system and random moves are proposed (with a translation scale
$\delta_0 = 0.05$).

For the larger system, SAMC parameter values of $t_0$ that gave rapid convergence for
the $N = 50$ system with $\delta = 0.05$ are too small.  Several additional
larger $t_0$ parameters are chosen to compare with SAD.  SAD has significantly smaller
fluctuations in the average entropy error for a given number of moves.

@@

A close examination of Fig.~\ref{fig:gamma-vs-t} shows that $\gamma$
for the Wang-Landau algorithm decreases much more rapidly than
$\nicefrac{1}{\sqrt{t}}$. It can be observed  for the simulations that were carried out that all the methods from
the weight-based family struggle to converge if the update factor decreases too rapidlly. Fig.~\ref{fig:n500-ff0.3} shows
WL and SAMC with inappropriate choices of $t_0$ i.e. less than
$\nicefrac{10^5}{\sqrt{t}}$ failing to converge in a reasonable amount
of time. Thus, the update factor $\gamma$, shown as a function of
simulation moves in Fig.~\ref{fig:gamma-vs-t}, proves useful in
determining which methods will converge in a reasonable amount of time.
We compare each method to a `golden' standard SAMC simulation for an ideal choice of $t_0$.  This gives an
unbiased comparison with our developed method SAD. The dynamic version
of SAMC which we call SAD performs as well as SAMC (assuming the user
can correctly identify an appropriate choice of $t_0$ for SAMC).  SAD
outperforms WL and WL-TMMC for the same given number of moves. The
absence of user defined parameters makes SAD an exciting alternative to
methods where user experience or successive implementation iteration
are needed to achieve reasonable results.

>>>>

@@

Both weight-based and transition matrix methods calculate
the density of states $D(E)$ for discrete energy
levels~\cite{haber2018performance}. For this reason, energy binning
becomes an important consideration for complex continous systems.
Energy bins are typically of uniform size for the entire energy
continuum~\cite{fasnacht2004adaptive}. Some methods such as
AdaWL~\cite{koh2013dynamically}
employ a tunable mechanism for controlling the binning for low entropic
states in order to ensure the exploration of all energies.  The method
introduced in this paper is designed to scale appropriately as bin size
is changed, but we do not test this scaling, as we use a system with
discrete energy levels.

@@

\subsection{SAMC}
The Stochastic Approximation Monte Carlo (SAMC) algorithm addresses
the lack of convergence of Wang-Landau's approach with a simple
schedule by which the update factor $\gamma$ is continuously
decreased~\cite{liang2007stochastic, werlich2015stochastic,
  schneider2017convergence}.  The update factor is defined in the
original implementation~\cite{liang2007stochastic} in terms of an
arbitrary tunable parameter $t_0$.
\begin{align}
\gamma_{t}^{\text{SA}} =\frac{t_0}{\max(t_0,t)}
\end{align}
where as above $t$ is the number of moves that have been attempted.
The major advantage that SAMC offers is its proven convergence.
Provided the update factor satisfies
\begin{align}
\sum_{t=1}^\infty \gamma_{t} = \infty \quad\textrm{and}\quad
\sum_{t=1}^\infty \gamma_{t}^\zeta < \infty
\end{align}
where $\zeta \in \{1,2\}$, Liang has shown that the weights are proven
to converge to the true density of states~\cite{liang2006theory,
  liang2007stochastic}.  In addition, the energy range need not be
known a priori.  The time to converge depends only on the choice of
parameters $t_0$.  Unfortunately, there is no
prescription for finding an acceptable value for $t_0$, and
while the algorithm formally converges, for a poor choice of $t_0$
that convergence can be far too slow to be practical.
Liang et al. give a rule of thumb in which $t_0$
is chosen in the range from $2N_S$ to $100N_S$ where $N_S$ is the number
of energy bins~\cite{liang2007stochastic}.  Schneider et al. found
that for the
Ising model this heuristic is helpful for small spin
systems, but that larger systems require an even higher $t_0$
value~\cite{schneider2017convergence}.  We find that for the square-well
fluid also $t_0$ in some cases needs to be two orders of magnitude higher
than the rule of thumb of $100N_S$.

Werlich \emph{et al.} proposed scaling the SAMC $\gamma_t$ by a factor
$\gamma_0$.  While this may result in an improved rate of convergence,
it adds yet another parameter that must be empirically determined, and
we have not explored this degree of freedom.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/N50-lndos-comparison}
  \caption{The entropy of a square well fluid with 50 atoms and filling fraction
        0.3 as the green line.  The green hatched area reflects the
        minimum entropy change needed to converge to the true value.
        The light blue area is the quadratic approximation
        for the change in entropy.  The vertical dotted lines represent
        the energy corresponding to $T=0.2$ and $T=\infty$.}
\end{figure}

@@

Figure~\ref{fig:gamma-vs-t} compares $\gamma_t$ for SAD, WL,
and SAMC.  The update factor
for WL remains high for many iterations, and then decreases very rapidly,
while the SAMC $\gamma_t$ remains constant before dropping as $1/t$.
The update factor for SAD in contrast fluctuates
dynamically around a value less than 1 for early MC moves.
{\color{red} For intermediate MC moves, $\gamma_t$ decreases as
$1/t$ while continuing to fluctuate whenever a new important energy
is discovered.  Once all the important energy states are discovered, the
update factor decreases faster than $1/t$ until asymptoting to $N_S/t$.
}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n500}
  \caption{The update factor $\gamma_t$ for $N=500$ versus iteration for three
    different methods: WL, SAMC, and SAD.
    method.}\label{fig:gamma-vs-t}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{The update factor $\gamma_t$ for $N=50$ versus iteration for three
    different methods: WL, SAMC, and SAD.}
\end{figure}

@@

A significant advantage of SAD over other flat histogram methods is
that energy binning is solved dynamically. SAD should perform
independently for a reasonable range of binning because $\gamma \propto
\nicefrac{N_S}{t}$.  As the number of energy states found $N_S$
increases (fine binning), the time spent $t$ in each bin will decrease.
This argument explains why SAD should perform well for complex systems
in terms of binning. SAMC has a prefactor $\gamma_0$ to aid in a
similar way but this adds yet another parameter for the user to choose.

@@

\subsection{Convergence}
Because SAD scales as $1/t$ for large $t$, it satisfies the SAMC
convergence criteria.  However, we also want to ensure that SAD avoids
the exponentially poor convergence time that SAMC suffers when $t_0$ is
small as discussed in Section~\ref{sec:samc-convergence}.
To place a lower bound on the convergence of SAD, we will again
approximate the total entropy change using an integral.  To sidestep
the dynamical nature of SAD, we ensure that \emph{after discovering the
last important energy} at time $t_L$ the entropy change
$\Delta S_{\text{tot}}$ can be made in a reasonable number of iterations.
Thus we integrate the update factor from $t_L$ to some minimum time
$t_{\min}$ necessary for convergence.  Technically this is not a lower
bound as in the case of SAMC because the algorithm will already have a
reasonable approximation for the entropy.
\begin{align}
\Delta S_{\text{tot}} &= \int_{t_L}^{t_{\min}}
     \frac{
       3\langle S\rangle + \frac{t}{t_L}
     }{
       3\langle S\rangle + \frac{t}{N_S}\frac{t}{t_L}
     } dt \\
&\approx 3\Delta S_{\text{tot}} \left(1-\frac{t_L}{t_{\min}}\right)
\end{align}
where we assumed that $t_L\gg N_S\langle S\rangle$, which is to say
that it takes a long time to find all the interesting energy states.
Furthermore, we omitted the $\frac{t}{t_L}$ in the numerator, which is
of order unity.  This omission only makes our bound more conservative,
and enables us to solve to find that
\begin{align}
  t_{\min} &= \frac32 t_L
\end{align}
which means that we only need to run fifty percent longer after we
discover the final interesting energy state in order to have made
sufficient updates to \emph{possibly} converge to the true entropy.

@@

For the square-well fluid, our simulations treat systems with a
well-width of $\lambda = 1.3$ and a filling fraction of
$\eta = 0.3$. We also explore various translation scales $\delta_0 = 0.005R$ and
$0.05R$. The simulations explore the
energy space of the systems at reduced temperatures of
$T_{\text{min}} = 0.2$ and $0.5$.  All simulations lead to the minimum important
energy $E_{\min}$ and maximum entropy energy $E_{\max}$
being calculated (with the exception of the WL methods where both
of these parameters are needed a priori).  In the sections below, we
examine the systems parameters impact on the convergence of the methods.

We use the average entropy error vs moves as a metric to compare
simulation runtimes and overall convergence. The overall accuracy
is determined by examining the fractional error of a particular method to
a precise reference system. For each simulation, the reference system
is chosen to be the final output of the SAMC simulation with the best
choice of $t_0$.
\begin{align}
\epsilon_\text{avg} = 1 - \bigg\lvert\frac{S_\text{method}}{S_\text{ref}}\bigg\rvert
\end{align}
Simulations that take more iterations to reach the same entropy error as a
different method take longer to converge. This behavior is seen in
Fig.~\ref{fig:N50-ff0.3-avg-error}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/3$ with
  SAMC $t_0 = 10^5$ serving as the reference.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-slow.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/3$ with
  SAMC $t_0 = 10^5$ from Fig.~\ref{fig:N50-ff0.3-avg-error}
  serving as the reference.}\label{fig:N50-ff0.3-avg-error-slow}
\end{figure}
%\begin{figure}
  %\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-fast.pdf}
  %\caption{The average entropy error for each method is shown for $\eta = 0.3$ with
  %SAMC followed by TMMC serving as the reference system.}\label{fig:N50-ff0.3-avg-error-fast}
%\end{figure}

\subsection{A periodic system with 50 atoms}

Figure~\ref{fig:N50-ff0.3-avg-error} shows the average entropy vs moves
for a system consisting of 50 atoms that are placed in a periodic
simple cubic unit cell with lattice constant chosen to give a filling
fraction of $\eta = 0.3$.  These particles are randomly inserted into
the system and random moves are proposed (with a translation scale
$\delta_0 = 0.05R$). For the $\eta = 30\%$ and $N = 50$ system, we
explore the choice of $\delta_0$ as a parameter.

{\color{red}
$S_{\max} = 120$ and $S_{\min} = 265$ for this system.  The number of
important energy states for this system is then $N_S = S_{\min} - S_{\max} = 145$.
The reduced temperature of $1/3$ is chosen in order to examine the convergence
properties of SAD in a reasonable simulation time.
}

Smaller translation
scales cause the given method to take additional time to explore all
energies. Ideal methods should scale linearly with the $\delta_0$, that
is, a decrease in the translation scale should result in a proportional
increase in convergence time. However, as can be seen from
Fig.~\ref{fig:N50-ff0.3-avg-error-slow} SAMC methods that rapidly
converged for $\delta = 0.05R$ do not proportionaly converge for a
translation scale of $\delta = 0.005R$. We see that SAD handles
arbitrary translation scales and proportionaly converges based on the
translation scale that is chosen.

\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/2$ with
  SAMC $t_0 = 10^6$ serving as the reference.}\label{fig:n500-ff0.3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/N500-lndos-comparison}
  \caption{Use this to create description of the system.}\label{fig:n500-lndos-comparison}
\end{figure}

\subsection{A periodic system with 500 atoms}

A system is configured with dimensions $x = y = z = 19\sigma$.  A
filling fraction $\eta = 0.3$ is chosen which yields $N = 500$
particles in a cubical lattice system.  These particles are randomly
inserted into the system and random moves are proposed (with a
translation scale $\delta_0 = 0.05R$).

{\color{red}
$S_{\max} = 1206$ and $S_{\min} = 2606$ for this system.  The number of
important energy states for this system is then $N_S = S_{\min} -
S_{\max} = 1400$. The reduced temperature of $1/2$ is chosen for the
larger system in order to examine the convergence properties of SAD in
a reasonable simulation time.
}

For the larger system, SAMC parameter values of $t_0$ that gave rapid
convergence for the $N = 50$ system with $\delta = 0.05R$ do not
converge rapidly.  Several additional larger $t_0$ parameters are
chosen to compare with SAD.  SAD has significantly smaller fluctuations
in the average entropy error for a given number of moves.

{\color{red}
Figure~\ref{fig:n500-lndos-comparison} shows the calculated entropy for
the $N = 500$ system. The grey dash lines indicate the $S_{\max} = 1206$
point and the $S_{\min} = 2606$. Only the reference method is shown.
}

@@

A close examination of Fig.~\ref{fig:gamma-vs-t} shows that $\gamma$
for the Wang-Landau algorithm decreases much more rapidly than
$\nicefrac{1}{\sqrt{t}}$. It can be observed  for the simulations that
were carried out that all the methods from the weight-based family
struggle to converge if the update factor decreases too rapidlly.
Fig.~\ref{fig:n500-ff0.3} shows WL and SAMC with inappropriate choices
of $t_0$ i.e. less than $\nicefrac{10^5}{\sqrt{t}}$ failing to converge
in a reasonable amount of time. Thus, the update factor $\gamma$, shown
as a function of simulation moves in Fig.~\ref{fig:gamma-vs-t}, proves
useful in determining which methods will converge in a reasonable
amount of time. We compare each method to a reference SAMC
simulation for an ideal choice of $t_0$.  This gives an unbiased
comparison with our developed method SAD. The dynamic version of SAMC
which we call SAD performs as well as SAMC (assuming the user can
correctly identify an appropriate choice of $t_0$ for SAMC).  SAD
outperforms WL and WL-TMMC for the same given number of moves. The
absence of user defined parameters makes SAD an exciting alternative to
methods where user experience or successive implementation iteration
are needed to achieve reasonable results.
